---
title: 'Intro to Network Analysis: igraph tutorial'
output:
  pdf_document: default
  html_document: default
---

##Install and load the required packages
```{r}
if (!requireNamespace("igraph", quietly = TRUE))
    install.packages("igraph")
library(igraph)

if (!requireNamespace("ggplot2", quietly = TRUE))
    install.packages("ggplot2")
library(ggplot2)
```


##Import the data.
If it isn't saved on your desktop, change the path (i.e. the file location) to where you have your data saved.
In this case, we import a file, 'yeast.csv', and assign it to the variable edgelist. 
```{r}
setwd("../Desktop")
edgelist <- read.csv("yeast.csv")

```

##Make a network.
Using the function graph_from_data_frame() we can make an igraph network object to run our analysis on and visualise.

```{r}
network <- graph_from_data_frame(edgelist, directed = F)

print(paste("Avg path length:", average.path.length(network))
      )

distr <- degree.distribution(network)

ggplot(data = data.frame(distr = distr[2:length(distr)],
                         "Degree" = as.factor(c(1:(length(distr)-1)))),
       aes(x = Degree, y = distr)) +
  geom_point() + geom_line(group = 1) + theme_minimal() +
  scale_y_continuous(name = "Degree Distribution")

deg <- degree(network)
plot(network, edge.arrow.size=.4,vertex.label=NA,
     vertex.size = deg, layout = layout_with_gem(network),
     main = "Network. Node size proportional to degree (k)")

hs <-hub_score(network, weights=NA)$vector
plot(network, edge.arrow.size=.4,vertex.label=NA,
     vertex.size = hs*10, layout = layout_with_gem(network),
     main = "Network. Node size proportional to hub score")
```

##Module Detection
Using the cluster_louvain function, we can find modules (areas of densley connected nodes) within our network.
Louvain is just one of the clustering algorithms that you can use from igraph.
Run ?cluster_ to read about the others
```{r}

groups <- cluster_louvain(network)

V(network)$groups <- membership(groups)

plot(network, 
     edge.arrow.size=.4,vertex.label=NA,
     vertex.size = 3.5, layout = layout_with_gem(network),
     vertex.color = V(network)$groups)

```

##Layouts
Layouts describe where your nodes are positioned in relation to one another.

```{r}
layout <- list(layout_nicely(network),
               layout_with_kk(network),
               layout_with_gem(network),
               layout_as_star(network),
               layout_as_tree(network),
               layout_with_dh(network)
               )

lapply(layout, function(x)
  plot(network, edge.arrow.size=.4,vertex.label=NA,
     vertex.size = 0.5, layout = x)
  )

```
